Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-08-25 awipev-CO2.Rmd
minor edits
table+ fig vertical sal gradient

- 1 SBE45 inside the Ferrybox (sal_fb)
- 5 CTD > 8 m depth (sal_insitu_ctd)

@@

df <- d_all %>% 
  dplyr::select(datetime, sal_insitu_ctd_1m, sal_insitu_ctd_3m, sal_insitu_ctd_5m, sal_insitu_ctd_7m, sal_insitu_ctd_9m) %>%
  dplyr::mutate(date = format(datetime, '%Y-%m-%d')) %>% 
  group_by(date) %>% 
  summarize(mean1m = mean(sal_insitu_ctd_1m, na.rm = TRUE),
            mean9m = mean(sal_insitu_ctd_9m, na.rm = TRUE),
            range = mean(sal_insitu_ctd_1m, na.rm = TRUE)-mean(sal_insitu_ctd_9m, na.rm = TRUE)) %>% 
  ungroup()
```
There are `r sum(!is.na(df$range))` days with salinity values at both 1 m (0-2 m) and 9 m (> 8 m). The salinity difference between 1 and 9 m ranges between `r min(df$range, na.rm=TRUE)` and `r max(df$range, na.rm=TRUE)` (mean: `r mean(df$range, na.rm=TRUE)`; `r median(df$range, na.rm=TRUE)`). The difference with depth is therefore significant.

@@

## Save files

>>>>

+ 1 SBE45 inside the Ferrybox (sal_fb)
+ 5 CTD > 8 m depth (sal_insitu_ctd)

@@

df <- d_all %>% 
  dplyr::select(datetime, sal_insitu_ctd_1m, sal_insitu_ctd_3m, sal_insitu_ctd_5m, sal_insitu_ctd_7m, sal_insitu_ctd_9m) %>%
  dplyr::mutate(date = format(datetime, '%Y-%m-%d')) %>% 
  group_by(date) %>% 
  summarize(mean1m = mean(sal_insitu_ctd_1m, na.rm = TRUE),
            mean9m = mean(sal_insitu_ctd_9m, na.rm = TRUE),
            range = mean(sal_insitu_ctd_1m, na.rm = TRUE)-mean(sal_insitu_ctd_9m, na.rm = TRUE)) %>% 
  ungroup()

p_sal_range <- ggplot(data = df) +
  geom_histogram((aes(x = df$range))) +
  labs(title = "Salinity difference between 1 and 9 m", x = "Difference") +
  Mytheme(size_labs = 8)
p_sal_range

quantile(df$range, na.rm = TRUE)
```
There are `r sum(!is.na(df$range))` days with salinity values at both 1 m (0-2 m) and 9 m (> 8 m). The salinity difference between 1 and 9 m ranges between `r min(df$range, na.rm=TRUE)` and `r max(df$range, na.rm=TRUE)` (mean: `r mean(df$range, na.rm=TRUE)`; `r median(df$range, na.rm=TRUE)`). The difference with depth is therefore significant.

@@
